---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# topicdoc

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/doug-friedman/topicdoc.svg?branch=master)](https://travis-ci.org/doug-friedman/topicdoc)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/doug-friedman/topicdoc?branch=master&svg=true)](https://ci.appveyor.com/project/doug-friedman/topicdoc)
[![Codecov test coverage](https://codecov.io/gh/doug-friedman/topicdoc/branch/master/graph/badge.svg)](https://codecov.io/gh/doug-friedman/topicdoc?branch=master)
<!-- badges: end -->

Like a (good) doctor, the goal of topicdoc is to help diagnose issues with your topic models through a variety of 
different diagnostics and metrics. There are a lot of great R packages for fitting topic models, but not a lot that
help evaluate their fit. This package seeks to fill that void with functions that easily allow you to run those
diagnostics/metrics efficiently on a variety of topic models.

## Installation

You can install the development version of topicdoc from [Github](https://www.github.com/doug-friedman/topicdoc) with:

``` r
remotes::install.packages("doug-friedman/topicdoc")
```

## Example

This is a simple use case - using an LDA model with 1992 Associated Press Dataset in `topicmodels`. 

```{r example}
library(topicdoc)
library(topicmodels)

data("AssociatedPress", package = "topicmodels")
lda <- LDA(AssociatedPress[1:100,], 
           control = list(seed = 33), k = 4)

# See the top 10 terms associated with each of the topics
terms(lda, 10)

# Calculate all diagnostics for each topic in the topic model
topic_diagnostics(lda, AssociatedPress[1:100,])

# ...or calculate them individually
topic_size(lda)
```

## Metrics Included
| Metric                                          |      Function       |  Description                                |
|:-----------------------------------------------:|:-------------------:|:-------------------------------------------:|
| topic size                                      | `topic_size`        | Total (weighted) number of tokens per topic |
| mean token length                               | `mean_token_length` | Average number of characters for the top tokens per topic |
| distance from corpus distribution               | `dist_from_corpus`  | Distance of a topic's token distribution from the overall corpus token distribution |
| distance between token and document frequencies | `tf_df_dist`        | Distance between a topic's token and document distributions |
| document prominence                             | `doc_prominence`    | Number of unique documents where a topic appears
| topic coherence                                 | `topic_coherence`   | Measure of how often the top tokens in each topic appear together in the same document |
| topic exclusivity                               | `topic_exclusivity` | Measure of how unique the top tokens in each topic are compared to the other topics |

## Key References

The following documents provide key references for the diagnostics/metrics included in the package.

* [Jordan Boyd-Graber, David Mimno, and David Newman, 2014.
Care and Feeding of Topic Models: Problems, Diagnostics, and Improvements.
CRC Handbooks of Modern Statistical Methods. CRC Press, Boca Raton, Florida.](http://www.people.fas.harvard.edu/~airoldi/pub/books/b02.AiroldiBleiEroshevaFienberg2014HandbookMMM/Ch12_MMM2014.pdf)
* [MALLET Topic Model Diagnostics](http://mallet.cs.umass.edu/diagnostics.php)
