---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# topicdoc

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/doug-friedman/topicdoc.svg?branch=master)](https://travis-ci.org/doug-friedman/topicdoc)
<!-- badges: end -->

Like a (good) doctor, the goal of topicdoc is to help diagnose issues with your topic models through a variety of 
different diagnostics and metrics. There are a lot of great R packages for fitting topic models, but not a lot that
help evaluate their fit. This package seeks to fill that void with functionality that easily allow you to run those
diagnostics/metrics efficiently on a variety of topic models.

## Installation

You can install the development version of topicdoc from [Github](https://www.github.com/doug-friedman/topicdoc) with:

``` r
remotes::install.packages("doug-friedman/topicdoc")
```

## Example

This is a basic use case - using the example model from `LDA` in `topicmodels`. 

```{r example}
library(topicdoc)
library(topicmodels)

data("AssociatedPress", package = "topicmodels")
lda <- LDA(AssociatedPress[1:20,], control = list(alpha = 0.1), k = 2)

# See the top 10 terms associated with each of the two topics
terms(lda, 10)

# Calculate the size (or fractional number of tokens) associated with each topic
topic_size(lda)

# Calculate the mean token length associated with each topic
mean_token_length(lda)
```


## Key References

The following documents provide key references for the diagnostics/metrics included in the package.

* [Jordan Boyd-Graber, David Mimno, and David Newman, 2014.
Care and Feeding of Topic Models: Problems, Diagnostics, and Improvements.
CRC Handbooks ofModern Statistical Methods. CRC Press, Boca Raton, Florida.](http://www.people.fas.harvard.edu/~airoldi/pub/books/b02.AiroldiBleiEroshevaFienberg2014HandbookMMM/Ch12_MMM2014.pdf)
* [MALLET Topic Model Diagnostics](http://mallet.cs.umass.edu/diagnostics.php)
